---
title: "JMJPFU_Clustering"
output: html_notebook
---

# JMJPFU
### 13-Feb-2017

In this Notebook, we will try out Non Supervised learning methods for the problem. We will try to do the following

1. Clustering models - KNN & Hierarchical clustering
2. Transformation of data set and observation of results
3. Tuning of the KNN & Hierarchical clustering models 
4. Association mining of the data set.


## Clustering Models - KNN

Let us start with the KNN models


### Initial tasks : Loading the library files

```{r}
library(caret)
library(dplyr)
library(ggplot2)
```

### Step 1 : Defining the Train control and metrics

```{r}
trainCon <- trainControl(method="repeatedcv",number=10,repeats = 3)

metric = "Accuracy"
```

### Step 2 : Building the baseline model

```{r}
seed = 7
set.seed(seed)

# Building the model

knnModel <- train(label~.,data=xTrain,metric=metric,method='knn',trControl=trainCon)

summary(knnModel)

```

### Step 3 : First prediction with the baseline model

```{r}
set.seed(seed)

# Prediction

knnpred <- knn3Train(xTrain[,1:11],xVal[,1:11],xTrain$label,k=9,prob=FALSE) # K=9 is an arbitary K which was used

# Doing the confusion matrix

confusionMatrix(knnpred,xVal$label)
```

As seen from the predictions, the accuracy and sensitivity values of all other classes are not that promising. We will try tuning the model and checking the results.

# Tomorrow

1. Continue with tuning of KNN
2. Explore other methods of clustering